---
name: Henrique
surname: Sposito
position: Computational Social Scientist
about: ""
orcid: "0000-0003-3420-6085"
email: henrique.sposito@graduateinstitute.ch
github: henriquesposito
www: henriquesposito.com
headcolor: "556B2F"
output:
  vitae::awesomecv:
    page_total: true
header-includes:
- \geometry{top=2cm, bottom=2cm}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
                      fig.pos = "H", out.extra = "")
library(vitae)
library(tibble)
library(kableExtra)
```

# Profile

My research leverages advanced text analysis techniques, such as supervised machine learning, to comparatively investigate diverse aspects of political discourses. I also develop, contribute, and maintain several R packages that assist researchers conducting social network analysis and connecting global governance data across domains. I am broadly interested in issues related to political discourse and environmental politics in Latin America.

\textbf{Interests:} Political Sociology, Environmental Politics, Text Analysis, Comparative Politics, Social Networks

# Education

```{r}
tribble(~ Degree, ~ Year, ~ Institution, ~ Where, ~ Why,
  "PhD in International Relations and Political Science",
  "Sep 2019 - Oct 2024",
  "The Graduate Institute of International and Development Studies", 
  "Geneva, Switzerland",
  "Doctoral Project: 'On doing politics: Authenticity, Problem-Construction, and Urgency in Political Discourse' \\\\ Supervised by Dr. James Hollway and Dr. Yanina Welp",
  "Masters in International Relations and Political Science",
  "Sep 2017 - Aug 2019",
  "The Graduate Institute of International and Development Studies",
  "Geneva, Switzerland",
  "Masters' Thesis: 'The Construction of a Migrant Crisis - The Venezuelan Migration to Brazil' \\\\ Supervised by Dr. Melanie Kolbe and Dr. Graziella Moraes Silva",
  "Bachelor of Arts in Political Science and Sociology (Double Degree)", "Jan 2013 - Jun 2017", "University of Alabama at Birmingham", "Birmingham, United States",
  "Recipient of 4 years of scholarship as a Student-Athlete for Soccer in a NCAA Division 1 University") %>% 
  detailed_entries(Institution, Year, Degree, Where, Why, .protect = FALSE)
```

# Publications and Working Papers

```{r}
tribble(~ Title, ~ Published, ~ Journal, ~ When,
        "\\href{https://journals.sagepub.com/doi/10.1177/00323217241261229}{Radiating Truthiness: Authenticity performances in politics in Brazil and the United States}", "\\href{https://journals.sagepub.com/doi/10.1177/00323217241261229}{DOI: 10.1177/00323217241261229}", "Political Studies", "July 2024",
  "\\href{https://www.tandfonline.com/doi/full/10.1080/09644016.2023.2220639}{Which Amazon Problem? Problem-constructions and Transnationalism in Brazilian Presidential Discourse since 1985 (with Livio Silva-Muller)}",
  "\\href{https://www.tandfonline.com/doi/full/10.1080/09644016.2023.2220639}{DOI: 10.1080/09644016.2023.2220639}", "Environmental Politics", "June 2023",
  "Public Acceptance of Environmental Restrictions in Non-Democratic Regimes (with Stefano Jud and Quynh Nguyen)",
  "Under review", "", "",
  "How urgent are your priorities? Comparing political priorities in discourse (with Jael Tan and James Hollway)",
  "Under review", "", "",
  "Armed Conflict and land-use dynamics: A global comparative analysis (with Remo Agovic, Stefano Jud, and Quynh Nguyen)",
  "Working Paper", "", "",
  "Universal Rules or Special Exceptions? Fairness and public support for climate policy in non-democratic settings (with Stefano Jud and Quynh Nguyen)",
  "Working Paper", "", "",
  "Does democratic backsliding defund the liberal world order? The case of the United Nations (with Livio Silva-Muller)", 
  "Working Paper", "", "",
  "Managing imprecise dates in R with messydates (with James Hollway)",
  "Working Paper", "", "") %>% 
  detailed_entries(where = Journal, with = Title, what = Published, when = When,
                   .protect = FALSE)
```

# Employment History (selected)

```{r}
tribble(~ What, ~ When, ~ With, ~ Where, ~ Why,
        "Postdoctoral Researcher in Environmental Governance and Global Development",
        "Nov 2024 - Present",
        "Wyss Academy for Nature at the University of Bern",
        "Bern, Switzerland",
        "Engage in the research, design, and formulation of innovative and sustainable governance solutions for people and nature
        \\item Lead an interdisciplinary research project mapping and analyzing environmental networks to identify new entry points for governance interventions and measure their impact over time
        \\item Evaluate the viability and effectiveness of possible solutions to pressing environmental challenges using state-of-the-art quantitative and qualitative research methods",
        "Research Assistant",
        "Sep 2020 - Aug 2024","Centre for International Environmental Studies", "Geneva, Switzerland",
        "Assisted with the theoretical, methodological, and empirical developments for comparing data across various issue-domains of global governance in the PANARCHIC project, funded by the Swiss National Science Foundation
        \\item Developed the data infrastructure and statistical methods in R for gathering, consolidating, and analyzing global governance data
        \\item Trained and managed research assistants collecting data, working with GitHub, designing websites, and contributing to diverse R packages",
        "Football Head Coach", "May 2018 - Aug 2020", "Intersoccer", "Geneva, Switzerland",
        "Ensured a safe and constructive environment for participants, coaches, and parents while promoting the benefits of sports
        \\item Supervised coaches and participants throughout activities to assure their safety
        \\item Coordinated and solved logistical issues related to transportation, venue organization, delivery of supplies, and medical emergencies") %>%
  detailed_entries(What, When, With, Where, Why, .protect = FALSE)
```

# Teaching

```{r}
tribble(~ Course, ~ Where, ~ Date, ~ Why,
        "Intermediate R for Social Science Research",
  "The Graduate Institute of International and Development Studies",
  "Fall 2023",
  "Provides an overview of various research methods using R
  \\item Teaches students how to carry-on different types of statistical modeling; how to work with unsupervised text analysis approaches; and how to analyze and visualize survey data
  \\item Encourages students to design their own research projects using R",
  "Fundamentals of R (co-lecturer)",
  "The Graduate Institute of International and Development Studies",
  "Fall 2022, Spring 2023, Fall 2023",
  "Provides a hands-on introduction to data science using the R programming language and software
  \\item Teaches students how to import, transform, analyze, and visualize various types of data in R
  \\item Demonstrates practical applications of R for the analysis of environment, finance, and conflict data") %>% 
  detailed_entries(what = Where, with = Course, where = Date, why = Why, .protect = FALSE)
```

# Invited Talks

```{r}
tribble(~ Title, ~ Talk, ~ Where, ~ Date, ~ Type,
        "Can (political) authenticity be performed?",
  "Faculté des hautes études commerciales de l'Université de Lausanne",
  "Lausanne, Switzerland",
  "May 2025",
  "Invited talk at the Department of Organizational Behavior Research Seminar",
  "How has the Brazilian Amazon been Constructed as a Problem? Presidential Speeches and Transnational Politics since 1985",
  "The Graduate Institute of International and Development Studies",
  "Geneva, Switzerland",
  "October 2022",
  "Invited talk at the Centre for International Environmental Studies Seminar",
  "Anti-Political Correctness and Authenticity: Authenticity performances in politics in Brazil and the United States",
  "Université de Lausanne",
  "Lausanne, Switzerland",
  "March 2022",
  "Invited talk for the Research Group on Elections and Political Citizenship") %>%
  detailed_entries(what = Talk, with = Title, when = Date, where = Where,
                   why = Type, .protect = FALSE)
```

# Conference Presentations (selected)

```{r}
tribble(~ Title, ~ Conference, ~ Where, ~ Date, ~ Type,
  "Swiss Political Science Association",
  "How urgent is climate change for our leaders? Urgency analysis of political priorities",
  "Geneva, Switzerland",
  "January 2025",
  "Panel on 'Preferences' in the Development and Environment working group",
  "American Sociological Association",
  "Anti-PC and Authenticity: Authenticity performances in politics in Brazil and the United States",
  "Los Angeles, United States",
  "August 2022",
  "Regular session on the 'Party and its base: Understanding the relationship between political professionals and their audiences'",
  "Latin American Studies Association",
  "Amazonian Repertoires in Brazilian Presidential Discourse since 1985",
  "Online",
  "May 2022",
  "Panel on the 'Forest Managements Conservation and Agricultural Production'",
  "Swiss Political Science Association",
  "Performing Authenticity: Anti-Politically Correct Discourses in Brazil and the United
States",
  "Online",
  "February 2022",
  "Workshop session on 'Liberal Ideology and Cultural Backlash'",
  "Latin American Studies Association",
  "The Construction of a Migratory Crisis: The Venezuelan Migration to Brazil",
  "Online",
  "May 2020",
  "Panel on 'Las distintas violencias de las migraciones'") %>%
  detailed_entries(what = Conference, with = Title, when = Date,
                   where = Where, why = Type, .protect = FALSE)
```

# R  Packages

```{r}
tribble(~ Name, ~ Purpose, ~ Status,
        "\\href{https://github.com/henriquesposito/poldis}{poldis}",
        "\\href{https://github.com/henriquesposito/poldis}{Tools for analyzing political discourses over time}", 
        "Author",
        "\\href{https://manydata.ch/}{manydata}",
        "\\href{https://manydata.ch/}{Portal for global governance data}",
        "Contributor",
        "\\href{https://globalgov.github.io/messydates/}{messydates}",
        "\\href{https://globalgov.github.io/messydates/}{Extended Date/Time Formats}",
        "Contributor",
        "\\href{https://stocnet.github.io/manynet/}{manynet}",
        "\\href{https://stocnet.github.io/manynet/}{Make, manipulate, and map myriad networks}",
        "Contributor",
        "\\href{https://stocnet.github.io/migraph/}{migraph}",
        "\\href{https://stocnet.github.io/migraph/}{Tools for multimodal and multilevel network analysis}", 
        "Contributor",
        "\\href{https://globalgov.github.io/manypkgs/}{manypkgs}",
        "\\href{https://globalgov.github.io/manypkgs/}{Support the creation of new many packages}",
        "Contributor") %>%
  detailed_entries(what = Purpose, with = Name, where = Status,
                   .protect = FALSE)
```

# Other Publications

```{r}
tribble(~ Title, ~ Published, ~ Journal, ~ When,
        "\\href{https://www.wyssacademy.org/_files/ugd/970651_0ecb76a65ba94cf3a1dbeaf15dfd372a.pdf}{Stakeholder Network Analysis of the Nam Tien Provincial Protection Forest in Laos}", "Wyss Academy for Nature at the University of Bern", "", "February 2025",
        "\\href{https://globalchallenges.ch/issue/16/the-politics-in-anti-politically-correct-discourses/}{The politics in anti-politically correct discourses}", "Global Challenges, Issue 16 - Elections, What For?", "", "November 2024") %>% 
  detailed_entries(where = Journal, with = Title, what = Published, when = When,
                   .protect = FALSE)
```

# Awards and Honors

- [Best Paper in Amazonian Studies at the Latin American Studies Association for "Which Amazon Problem? Problem-constructions and Transnationalism in Brazilian Presidential Discourse since 1985"](https://lasaweb.org/en/2024-section-awards/)
- UAB Presidential Honors List 2013, 2015, 2016 and 2017
- Conference USA Commissioner's Honor Roll 2013 – 2016
- National Soccer Coaches Association of America NCAA Scholar All-South Region Team 2016
- Conference USA All-Academic Team 2016
- College Sports Information Directors of America Academic All-District Team 2016
- Conference USA Academic Honor Medal 2015

# Skills

- **Languages:** Portuguese (native); English (fluent); French (proficient); Italian (intermediate); Spanish (intermediate) 

- **Programming languages:** R (proficient); Python (intermediate); Java (intermediate), C (basic)

- **Markup languages:** Markdown (proficient); LaTeX (advanced); HTML (advanced); CSS (advanced)

# References

```{r}
tribble(~ Name, ~ Position, ~ Contact,
        "\\href{https://jameshollway.com/}{James Hollway}", 
        "Associate Professor of International Relations and Political Science
        \\newline Co-Director of the Global governance Centre
        \\newline The Graduate Institute of International and Development Studies",
        "Email: \\href{james.hollway@graduateinstitute.ch}{james.hollway@graduateinstitute.ch}",
        "\\href{https://www.graduateinstitute.ch/academic-departments/faculty/graziella-moraes-dias-da-silva}{Graziella Moraes Dias da Silva}", 
        "Associate Professor of Anthropology and Sociology
        \\newline Co-Director of the Albert Hirschman Centre on Democracy
        \\newline The Graduate Institute of International and Development Studies",
        "Email: \\href{graziella.moraes@graduateinstitute.ch}{graziella.moraes@graduateinstitute.ch}",
        "\\href{https://yaninawelp.wordpress.com/about-me/}{Yanina Welp}",
        "Research Fellow
        \\newline Albert Hirschman Centre on Democracy
        \\newline The Graduate Institute of International and Development Studies",
        "Email: \\href{yanina.welp@graduateinstitute.ch}{yanina.welp@graduateinstitute.ch}") %>%
  detailed_entries(what = Position, why = Contact,
                   with = Name, .protect = FALSE)
```
