---
name: Henrique
surname: Sposito
position: Researcher
about: ""
email: henrique.sposito@graduateinstitute.ch
github: henriquesposito
twitter: rickysposito
www: henriquesposito.com
headcolor: "556B2F"
output:
  vitae::awesomecv:
    page_total: true
header-includes:
- \geometry{top=1.75cm}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
                      fig.pos = "H", out.extra = "")
library(vitae)
library(tibble)
library(kableExtra)
```

# Profile

My research leverages advanced text analysis techniques, such as supervised machine learning, to investigate how authenticity, problem construction, and urgency appear and change over time and across settings in political discourses. I also develop, contribute, and help maintain several R packages that assist researchers dealing with multiple, overlapping, and uncertain datasets across various domains of global governance.

<!-- \centerline{Interests: Political Sociology, Statistical Methods, Environmental Studies} -->

# Education

```{r}
tribble(~ Degree, ~ Year, ~ Institution, ~ Where, ~ Why,
  "PhD in International Relations and Political Science",
  "Sep 2019 - 2024 (expected)",
  "The Graduate Institute of International and Development Studies (IHEID)", 
  "Geneva, Switzerland",
  "Doctoral Project: 'Authenticity, problem construction, and urgency in political discourses' \\\\ Supervised by Dr. James Hollway and Dr. Yanina Welp
  \\item Core Courses: Doctoral Seminar; Survey Experiments; Social Networks; Statistics; Identity and Violence",
  "Masters in International Relations and Political Science",
  "Sep 2017 - Aug 2019",
  "The Graduate Institute of International and Development Studies (IHEID)",
  "Geneva, Switzerland",
  "Masters' Thesis: 'The Construction of a Migrant Crisis - The Venezuelan Migration to Brazil' \\\\ Supervised by Dr. Melanie Kolbe and Dr. Graziella Moraes Silva",
  "Bachelor of Arts in Political Science and Sociology (Double Degree)", "Jan 2013 - Jun 2017", "University of Alabama at Birmingham", "Birmingham, United States",
  "Recipient of 4 years of scholarship as a Student-Athlete for Soccer in a NCAA Division 1 University") %>% 
  detailed_entries(Institution, Year, Degree, Where, Why, .protect = FALSE)
```

# Research Experience

```{r}
tribble(~ What, ~ When, ~ With, ~ Where, ~ Why,
        "Research Assistant",
        "Sep 2020 - Present","Center for International Environmental Studies (CIES)", "Geneva, Switzerland",
        "Assist with the theoretical, methodological, and empirical developments in data and analysis for across various domains of global governance in the 'PANARCHIC: Power and Networks and the Rate of Change in Institutional Complexes' project funded by the Swiss National Science Foundation (SNSF)
        \\item Help with the development data infrastructure and statistical methods in R, offered as an emsemble of R packages, for the gathering, consolidating, and analyzing global governance data
        \\item Train and manage research assistants to work with data colletion, R package development, GitHub branching, website design, and among other programmatic issues related to the project") %>%
  detailed_entries(With, When, What, Where, Why, .protect = FALSE)
# #long version (Selected Employment History)
# tribble(~ What, ~ When, ~ With, ~ Where, ~ Why,
#         "Research Assistant", "Sep 2020 - Present", "Center for International Environmental Studies (CIES)", "Geneva, Switzerland",
#         "Assist with the theoretical, methodological, and empirical developments in data and analysis for across various domains of global governance in the 'PANARCHIC: Power and Networks and the Rate of Change in Institutional Complexes' project funded by the Swiss National Science Foundation (SNSF)
#         \\begin{itemize}
#         \\item Help develop data infrastructure and statistical methods in R, offered as an emsemble of R packages, for the gathering, consolidation, and analysis of global governance data.
#         \\item Train and manage other research assistants to work with data colletion, R programming, package development, GitHub branching, and other theoretical and practical issues related to the project.
#         \\end{itemize}",
#         "Football Head Coach", "May 2018 - Aug 2020", "Intersoccer", "Geneva, Switzerland",
#         "Ensured a safe and constructive environment for participants, coaches, and parents while promoting the benefits of sports
#         \\begin{itemize}
#         \\item Supervised coaches and participants throughout activities to ensure their safety.
#         \\item Communicated with coaches, children, and parents to cordinate and solve logistical issues related to transportation, venue organization, and delivery of supplies, as well as any medical emergencies and other unexpected events that arose.
#         \\end{itemize}") %>%
#   detailed_entries(What, When, With, Where, Why, .protect = FALSE)
```

# Publications and Working Papers

```{r}
tribble(~ Title, ~ Published, ~ Journal, ~ When,
  "\\href{https://www.tandfonline.com/doi/full/10.1080/09644016.2023.2220639}{Which Amazon Problem? Problem-constructions and Transnationalism in Brazilian Presidential Discourse since 1985 (with Livio Silva-Muller)}",
  "\\href{https://www.tandfonline.com/doi/full/10.1080/09644016.2023.2220639}{DOI: 10.1080/09644016.2023.2220639}", "Environmental Politics", "June 2023",
  "Radiating Truthiness: Authenticity performances in politics in Brazil and the United States", "Under Review in Political Studies", "", "",
  "Managing imprecise dates in R with messydates (with James Hollway)",
  "Working Paper", "", "",
  "It is urgent that we look at urgency in politics: An introduction to urgency analysis",
  "Working Paper", "", "") %>% 
  detailed_entries(where = Journal, with = Title, what = Published, when = When,
                   .protect = FALSE)
```

# Teaching

```{r}
tribble(~ Course, ~ Where, ~ Date, ~ Why, 
  "Fundamentals of R (co-lecturered with Livio Silva-Muller)",
  "The Graduate Institute of International and Development Studies (IHEID)",
  "Fall 2022, Spring 2023, Fall 2023",
  "Provides a hands-on introduction to data science using the R programming language and software
  \\item Teaches students how to import, transform, analyze, and visualize various types of data in R
  \\item Demonstrates practical applications of R for the analysis of environment, finance, and conflict data",
  "Intermediate R for Social Science Research",
  "The Graduate Institute of International and Development Studies (IHEID)",
  "Fall 2023 (upcoming)",
  "Provides an applied introduction to various research methods using R
  \\item Teaches students how to select and carry-on different types of statistical modeling; how to work with unsupervised approaches for text analysis; and how to code, visualize, and model network data") %>% 
  detailed_entries(what = Where, with = Course, where = Date, why = Why, .protect = FALSE)
```

# Conference Presentations

```{r}
tribble(~ Title, ~ Conference, ~ Where, ~ Date, ~ Type,
  "Anti-PC and Authenticity: Authenticity performances in politics in Brazil and the United States",
  "American Sociological Association",
  "Los Angeles, United States",
  "August 2022",
  "Regular session on the 'Party and its base: Understanding the relationship between political professionals and their audiences'",
  "Amazonian Repertoires in Brazilian Presidential Discourse since 1985",
  "Latin American Studies Association",
  "Online",
  "May 2022",
  "Panel on the 'Forest Managements Conservation and Agricultural Production'",
  "Performing Authenticity: Anti-Politically Correct Discourses in Brazil and the United
States",
  "Swiss Political Science Association",
  "Online",
  "February 2022",
  "Workshop session on 'Liberal Ideology and Cultural Backlash'",
  "The Construction of a Migratory Crisis: The Venezuelan Migration to Brazil",
  "Latin American Studies Association",
  "Online",
  "May 2020",
  "Panel on 'Las distintas violencias de las migraciones'") %>%
  detailed_entries(what = Conference, with = Title, when = Date,
                   where = Where, why = Type, .protect = FALSE)
```

# Invited talks

```{r}
tribble(~ Title, ~ Talk, ~ Where, ~ Date, ~ Type,
  "How has the Brazilian Amazon been Constructed as a Problem? Presidential Speeches and Transnational Politics since 1985",
  "The Graduate Institute of International and Development Studies (IHEID)",
  "Geneva, Switzerland",
  "October 2022",
  "Invited talk at the Center for International Environmental Studies (CIES) Seminar",
  "Anti-Political Correctness and Authenticity: Authenticity performances in politics in Brazil and the United States",
  "Université de Lausanne",
  "Lausanne, Switzerland",
  "March 2022",
  "Invited talk for the Research Group on Elections and Political Citizenship (GREC)") %>%
  detailed_entries(what = Talk, with = Title, when = Date, where = Where,
                   why = Type, .protect = FALSE)
```

# Packages

```{r}
tribble(~ Name, ~ Purpose, ~ Status,
        "\\href{https://manydata.ch/}{manydata}",
        "\\href{https://manydata.ch/}{An R portal for global governance data}",
        "Contributor",
        "\\href{https://globalgov.github.io/messydates/}{messydates}",
        "\\href{https://globalgov.github.io/messydates/}{An R package for Extended Date/Time Format (EDTF)}",
        "Contributor",
        "\\href{https://snlab-ch.github.io/manynet/}{manynet}",
        "\\href{https://snlab-ch.github.io/manynet/}{An R package to make, manipulate, and map myriad networks}",
        "Contributor",
        "\\href{https://snlab-ch.github.io/migraph/}{migraph}",
        "\\href{https://snlab-ch.github.io/migraph/}{An R package with tools for multimodal and multilevel network analysis}", 
        "Contributor",
        "\\href{https://globalgov.github.io/manypkgs/}{manypkgs}",
        "\\href{https://globalgov.github.io/manypkgs/}{An R package to support the creation of new many packages}",
        "Contributor",
        "\\href{https://globalgov.github.io/manyenviron/}{manyenviron}",
        "\\href{https://globalgov.github.io/manyenviron/}{An R data package on environmental agreements}",
        "Contributor",
        "\\href{https://globalgov.github.io/manystates/}{manystates}",
        "\\href{https://globalgov.github.io/manystates/}{An R data package on sovereign states}",
        "Contributor",
        "\\href{https://github.com/henriquesposito/poldis}{poldis}",
        "\\href{https://github.com/henriquesposito/poldis}{An R package with tools for analyzing political discourses over time}", 
        "Author") %>%
  detailed_entries(what = Purpose, with = Name, where = Status,
                   .protect = FALSE)
```

# Awards and Honors

- UAB Presidential Honors List 2013, 2015, 2016 and 2017
- Conference USA Academic Honor Medal (2015)
- National Soccer Coaches Association of America NCAA Scholar All-South Region Team (2016)
- Conference USA Commissioner's Honor Roll (2013 – 2016)
- Conference USA All-Academic Team (2016)
- College Sports Information Directors of America Academic All-District Team (2016)

# Skills

<!-- ```{=latex} -->
<!-- \begin{table}[tbh] -->
<!-- \centering -->
<!-- \begin{tabular}{cccll} -->
<!-- \textbf{Languages} & \textbf{Programming languages} & \textbf{Markup languages} & \textit{} & \textit{} \\ -->
<!-- \multicolumn{1}{l}{}   & \multicolumn{1}{l}{}  & \multicolumn{1}{l}{}  &  &  \\ -->
<!-- Portuguese (Native)    & R (Proficient)        & Markdown (Proficient) &  &  \\ -->
<!-- English (Fluent)       & Python (Intermediate) & LaTeX (Advanced)      &  &  \\ -->
<!-- French (Proficient)    & C (Basic)             & HTML (Advanced)       &  &  \\ -->
<!-- Italian (Intermediate) & Bash (Basic)          & CSS (Intermediate)    &  &  \\ -->
<!-- Spanish (Basic)        & Java (Basic)          & XML (Basic)           &  &  \\ -->
<!--                        &                       &                       &  &  -->
<!-- \end{tabular} -->
<!-- \end{table} -->
<!-- ``` -->

- **Languages:** Portuguese (native); English (fluent); French (proficient); Italian (intermediate); Spanish (basic) 

- **Programming languages:** R (proficient); Python (intermediate); C (basic); Bash (basic); Java (basic)

- **Markup languages:** Markdown (proficient); LaTeX (advanced); HTML (advanced); CSS (intermediate)

# References

```{r}
tribble(~ Name, ~ Position, ~ Contact,
        "\\href{https://jameshollway.com/}{James Hollway}", 
        "Associate Professor of International Relations and Political Science \\newline The Graduate Institute of International and Development Studies (IHEID)",
        "Email: \\href{jameshollway@graduateinstitute.ch}{jameshollway@graduateinstitute.ch}",
        "\\href{https://yaninawelp.wordpress.com/about-me/}{Yanina Welp}",
        "Research Fellow \\newline Albert Hirschman Centre on Democracy (AHCD)",
        "Email: \\href{yaninawelp@graduateinstitute.ch}{yaninawelp@graduateinstitute.ch}") %>%
  detailed_entries(what = Position, why = Contact,
                   with = Name, .protect = FALSE)
```

\center{*Additional references available upon request*}
