---
name: Henrique
surname: Sposito
position: Researcher
phone: +41 79 761 6863
email: henrique.sposito@graduateinstitute.ch
website: henriquesposito.com
github: henriquesposito
twitter: rickysposito
headcolor: "556B2F"
output:
  vitae::awesomecv:
    page_total: true
header-includes:
- \usepackage{float}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
                      fig.pos = "H", out.extra = "")
library(vitae)
library(tibble)
library(kableExtra)
```

# Profile

I am currently a PhD candidate at the International Relations and Political Science Department at the Geneva Graduate Institute (IHEID). My dissertation leverages advanced text analysis techniques in R, such as Natural Language Processes (NLP) and supervised machine learning, to investigate how authenticity, problem construction, and urgency appear and change over time and across settings in discursive politics. I work as a Research Assistant in the "PANARCHIC: Power and Network and the Rate of Change in Institutional Complexes" project held at the Center for International Environmental Studies (CIES). For the project, I develop, contribute, and help maintain several R packages that assist researchers dealing with multiple, overlapping, and uncertain datasets across various domains of global governance. During my free time, I restore vintage bikes.

# Education

```{r}
tribble(~ Degree, ~ Year, ~ Institution, ~ Where, ~ Why,
  "Doctorate in International Relations and Political Science", "Sep 2019 - Sep 2023 (expected)", "The Graduate Institute of International and Development Studies (IHEID)", "Geneva, Switzerland",
  "GPA: 5.4/6
  \\begin{itemize}
     \\item Doctoral Project: 'Tell it how it is: Authenticity, setting, and urgency in political discourses' (Supervised by Dr. James Hollway and Dr. Yanina Welp)
     \\item Core Courses: Doctoral Seminar; Survey Experiments; Social Networks; Statistics; Identity and Violence
   \\end{itemize}",
  "Masters in International Relations and Political Science", "Sep 2017 - Aug 2019",
  "The Graduate Institute of International and Development Studies (IHEID)", "Geneva, Switzerland",
  "GPA: 5.18/6
   \\begin{itemize}
     \\item Masters' Thesis: 'The Construction of a Migrant Crisis - The Venezuelan Migration to Brazil' (Supervised by Dr. Melanie Kolbe and Dr. Graziella Moraes Silva; Grade: 5.25)
     \\item Core Courses: Research Design; Comparative Politics; Qualitative Methods; International Political Economy, Foreign Policy Analysis
   \\end{itemize}",
  "Bachelor of Arts in Political Science and Sociology (Double Degree) with a minor in Economics", "Jan 2013 - Jun 2017", "University of Alabama at Birmingham", "Birmingham, United States",
  "GPA: 3.85/4
   \\begin{itemize}
     \\item Core Courses: Research in Political Science; International Sociology; Behavioral Economics; Social Statistics; Mind, Self and Society; Human Rights
     \\item Recipient of 4 years of scholarship as a Student-Athlete for Soccer in a NCAA Division 1 University
   \\end{itemize}") %>% 
  detailed_entries(Degree, Year, Institution, Where, Why, .protect = FALSE)
```

# Selected Employment History

```{r}
tribble(~ What, ~ When, ~ With, ~ Where, ~ Why,
        "Research Assistant", "Sep 2020 - Present", "Center for International Environmental Studies (CIES)", "Geneva, Switzerland",
        "Assist with the theoretical, methodological, and empirical developments in data and analysis for across various domains of global governance in the project called 'Power and Networks and the Rate of Change in Institutional Complexes' (PANARCHIC), funded by the Swiss National Science Foundation (SNSF)
        \\begin{itemize}
        \\item Help develop data infrastructure and statistical methods in R, offered as an emsemble of R packages, for the gathering, consolidation, and analysis of global governance data.
        \\item Train and manage Masters' research assistants to work with data colletion, R programming and package development, GitHub branching, and other theoretical and practical issues related to the project.
        \\end{itemize}") %>%
  detailed_entries(What, When, With, Where, Why, .protect = FALSE)
# #long version
# tribble(~ What, ~ When, ~ With, ~ Where, ~ Why,
#         "Research Assistant", "Sep 2020 - Present", "Center for International Environmental Studies (CIES)", "Geneva, Switzerland",
#         "Assist with the theoretical, methodological, and empirical developments in data and analysis for across various domains of global governance in the project called 'Power and Networks and the Rate of Change in Institutional Complexes' (PANARCHIC), funded by the Swiss National Science Foundation (SNSF)
#         \\begin{itemize}
#         \\item Help develop data infrastructure and statistical methods in R, offered as an emsemble of R packages, for the gathering, consolidation, and analysis of global governance data.
#         \\item Train and manage Masters' research assistants to work with data colletion, R programming and package development, GitHub branching, and other theoretical and practical issues related to the project.
#         \\end{itemize}",
#         "Football Head Coach", "May 2018 - Aug 2020", "Intersoccer", "Geneva, Switzerland",
#         "Ensured a safe and constructive environment for participants, coaches, and parents while promoting the benefits of sports
#         \\begin{itemize}
#         \\item Supervised coaches and participants throughout activities to ensure their safety.
#         \\item Communicated with coaches, children, and parents to cordinate and solve logistical issues related to transportation, venue organization, and delivery of supplies, as well as any medical emergencies and other unexpected events that arose.
#         \\end{itemize}") %>%
#   detailed_entries(What, When, With, Where, Why, .protect = FALSE)
```

# Teaching

```{r}
tribble(~ Course, ~ Where, ~ Date, ~ Why, 
  "Fundamentals of R (co-lecturered with Livio Silva-Muller)",
  "The Graduate Institute of International and Development Studies (IHEID)",
  "Fall 2022, Spring 2023, Fall 2023",
  "This course offers masters' students a hands on introduction to data science using the R programming language and software. We teach students how to import, transform, analyze, and visualize various types of data in R. To help students think through data, we show practical applications of R for the analysis of environment, finance, and conflict data.",
  "Intermediate R for Social Science Research",
  "The Graduate Institute of International and Development Studies (IHEID)",
  "Fall 2023",
  "This course offers masters' students an applied overview of various research methods using R. Students learn how to write, cite, and include table and figures using R Markdown; how to select and carry-on different types of statistical modeling; how to work with unsupervised approaches for text analysis; and how to code, visualize, and model network data.") %>% 
  detailed_entries(what = Where, with = Course, when = Date, why = Why, .protect = FALSE)
```

# Publications

```{r}
tribble(~ Title, ~ Published, ~ Journal,  ~ Why, 
  "Which Amazon Problem? Problem-constructions and Transnationalism in Brazilian Presidential Discourse since 1985 (with Livio Silva-Muller)", "Published online on 14 Jun 2023", "Environmental Politics",
  "This article investigates how the Amazon has been constructed as a problem in Brazilian presidential speeches since 1985. We develop a framework that accounts for how important transnational actors, as presidents, construct policy objects as particular problems depending on where and when they participate in politics
  \\begin{itemize}
     \\item Methods: We create a dataset containing 6240 official speeches by all Brazilian presidents since 1985. We train a supervised machine learning algorithim to classify how Amazon related sections within speeches construct the Amazon as a problem.
     \\item Findings: We find that presidents often construct the Amazon as an environmental problem when speaking far away from the region, whereas they usually construct it as problems of economic integration or social development when in the Amazon.
   \\end{itemize}",
  "Radiating Truthiness: Authenticity performances in politics in Brazil and the United States", "Under Review", "Political Studies",
  "Political authenticity, as the perceived degree to which politicians appear to remain true to themselves, is connected to higher levels of political trust from electorates and can influence political outcomes. Yet, authenticity is frequently overlooked as a determinant factor for electoral behavior for being deemed vague, and, when considered, discussions of how authenticity appears and changes in politics usually remain at the theoretical level and are rarely comparative. This article develops an innovative framework to identify and compare how authenticity is performed in political discourses over time, across settings, and by politicians.
     \\begin{itemize} 
     \\item Methods: A total of 24,170 political texts from campaign rallies, debates, interviews, and official speeches for presidents and presidential candidates since the 1980s were scraped for Brazil and the United States, where authenticity in politics has drawn increased attention.
     \\item Findings: The findings indicate that authenticity is not performed more frequently in election years.
   \\end{itemize}") %>% 
  detailed_entries(when = Published, with = Title, what = Journal, why = Why,
                   .protect = FALSE)
```

# Selected Conference Presentations and Invited Talks

```{r}
# # short version
# tribble(~ Title, ~ Conference, ~ Where, ~ Date, ~ Type, 
#   "How has the Brazilian Amazon been Constructed as a Problem? Presidential Speeches and Transnational Politics since 1985",
#   "The Graduate Institute of International and Development Studies (IHEID)",
#   "Geneva, Switzerland",
#   "27 October 2022",
#   "Center for International Environmental Studies (CIES) seminars",
#   "Anti-PC and Authenticity: Authenticity performances in politics in Brazil and the United States",
#   "American Sociological Association",
#   "Los Angeles, United States",
#   "6 August 2022",
#   "Regular session on the 'Party and its base: Understanding the relationship between political professionals and their audiences'",
#   "Performing Authenticity: Anti-Politically Correct Discourses in Brazil and the United
# States",
#   "Swiss Political Science Association",
#   "Online",
#   "4 February 2022",
#   "Workshop session on 'Liberal Ideology and Cultural Backlash'") %>% 
#   detailed_entries(what = Conference, with = Title, when = Date, where = Where, 
#                    why = Type, .protect = FALSE)
# Longer version
tribble(~ Title, ~ Conference, ~ Where, ~ Date, ~ Type,
  "How has the Brazilian Amazon been Constructed as a Problem? Presidential Speeches and Transnational Politics since 1985",
  "The Graduate Institute of International and Development Studies (IHEID)",
  "Geneva, Switzerland",
  "27 October 2022",
  "Center for International Environmental Studies (CIES) seminars",
  "Anti-PC and Authenticity: Authenticity performances in politics in Brazil and the United States",
  "American Sociological Association",
  "Los Angeles, United States",
  "6 August 2022",
  "Regular session on the 'Party and its base: Understanding the relationship between political professionals and their audiences'",
  "Amazonian Repertoires in Brazilian Presidential Discourse since 1985",
  "Latin American Studies Association",
  "Online",
  "6 May 2022",
  "Panel on the 'Forest Managements Conservation and Agricultural Production'",
  "Anti-Political Correctness and Authenticity: Authenticity performances in politics in Brazil and the United States",
  "Université de Lausanne",
  "Lausanne, Switzerland",
  "31 March 2022",
  "Invited talk for the Research Group on Elections and Political Citizenship (GREC)",
  "Performing Authenticity: Anti-Politically Correct Discourses in Brazil and the United
States",
  "Swiss Political Science Association",
  "Online",
  "4 February 2022",
  "Workshop session on 'Liberal Ideology and Cultural Backlash'",
  "The Construction of a Migratory Crisis: The Venezuelan Migration to Brazil",
  "Latin American Studies Association",
  "Online",
  "15 May 2020",
  "Panel on 'Las distintas violencias de las migraciones'") %>%
  detailed_entries(what = Conference, with = Title, when = Date, where = Where,
                   why = Type, .protect = FALSE)
```

\newpage

# Skills

```{=latex}
\begin{table}[tbh]
\centering
\begin{tabular}{cccll}
\textbf{Languages} & \textbf{Programming languages} & \textbf{Markup languages} & \textit{} & \textit{} \\
\multicolumn{1}{l}{}   & \multicolumn{1}{l}{}  & \multicolumn{1}{l}{}  &  &  \\
Portuguese (Native)    & R (Proficient)        & Markdown (Proficient) &  &  \\
English (Fluent)       & Python (Intermediate) & LaTeX (Advanced)      &  &  \\
French (Advanced)      & C (Basic)             & HTML (Advanced)       &  &  \\
Italian (Intermidiate) & Bash (Basic)          & CSS (Advanced)        &  &  \\
Spanish (Basic)        & Java (Basic)          & XML (Basic)           &  &  \\
                       &                       &                       &  & 
\end{tabular}
\end{table}
```

***References available upon request.***
